A High Efficiency MAC Protocol for WLANs: Providing Fairness in Dense Scenarios

### 2015-10-07 introProtocol.tex
Started modifying the figures

\begin{figure}[tb]
\centering
  \includegraphics[width=0.7\linewidth, angle=-90]{figures/DCF-vs-ECA/DCF-vs-ECA2.eps}
  \caption{CSMA/ECA example in saturation: throughput (simulation parameters can be found in Section~\ref{simulations})}
  \label{fig:BECA}
\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth, angle=-90]{figures/fairness-combined/fairness-combined.eps}
		\caption{Fairness comparison with nodes under saturation (simulation parameters can be found in Section~\ref{simulations})}
		\label{fig:fairness}
	\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/throughput-combined/throughput-combined.eps}
		\caption{Throughput comparison~\cite{research2standards} (simulation parameters can be found in Section~\ref{simulations})}
		\label{fig:ECA+H+F-throughput}
	\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/throughput-max-Ag/throughput-saturated-maxAgg.eps}
		\caption{Throughput comparison with CSMA/CA$_{\text{MaxAg}}$: even though at low number of contenders CSMA/CA$_{\text{MaxAg}}$ achieves greater throughput than CSMA/ECA$_{\text{Hys+FS}}$, collisions eventually degrade the throughput below CSMA/ECA$_{\text{Hys+FS}}$'s when the number of contenders increases past $N=10$. \textcolor{red}{This figure should also show CSMA/CA$_{\text{FS}}$}.}
		\label{fig:ECA-vs-DCF-maxAgg}
	\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/fairness-max-Ag/fairness-maxAg-combined.eps}
		\caption{Fairness comparision when using maximum aggregation}
		\label{fig:fairness-with-maximum-aggregation}
	\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/throughput-w-model/throughput-combined-w-model4.eps}
		\caption{Upper and Lower throughput bounds for CSMA/ECA$_{\text{Hys+FS}}$}
		\label{fig:ECA-bounds-comparison}
	\end{figure}

>>>>

\begin{figure}[tb]
\centering
  \includegraphics[width=0.7\linewidth, angle=-90]{figures/DCF-vs-ECA/DCF-v-ECA-TON.eps}
  \caption{CSMA/ECA example in saturation: throughput (simulation parameters can be found in Section~\ref{simulations})}
  \label{fig:BECA}
\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth, angle=-90]{figures/fairness-combined/fairness-combined-TON.eps}
		\caption{Fairness comparison with nodes under saturation (simulation parameters can be found in Section~\ref{simulations})}
		\label{fig:fairness}
	\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/throughput-combined/throughput-combined-TON.eps}
		\caption{Throughput comparison~\cite{research2standards} (simulation parameters can be found in Section~\ref{simulations})}
		\label{fig:ECA+H+F-throughput}
	\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/throughput-max-Ag/throughput-saturated-maxAgg-TON.eps}
		\caption{Throughput comparison with CSMA/CA$_{\text{MaxAg}}$: even though at low number of contenders CSMA/CA$_{\text{MaxAg}}$ achieves greater throughput than CSMA/ECA$_{\text{Hys+FS}}$, collisions eventually degrade the throughput below CSMA/ECA$_{\text{Hys+FS}}$'s when the number of contenders increases past $N=10$. \textcolor{red}{This figure should also show CSMA/CA$_{\text{FS}}$}.}
		\label{fig:ECA-vs-DCF-maxAgg}
	\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/fairness-max-Ag/fairness-maxAg-combined-TON.eps}
		\caption{Fairness comparision when using maximum aggregation}
		\label{fig:fairness-with-maximum-aggregation}
	\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/throughput-w-model/throughput-combined-w-model-TON.eps}
		\caption{Upper and Lower throughput bounds for CSMA/ECA$_{\text{Hys+FS}}$}
		\label{fig:ECA-bounds-comparison}
	\end{figure}
